\documentclass{article}
\usepackage{inconsolata}
\usepackage{indentfirst}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage[T1]{fontenc}

\definecolor{cbackground}{rgb}{0.9, 0.9, 0.9}
\definecolor{cstring}{rgb}{0, 0.5, 0}

\lstset{language=C, upquote=true}
\lstdefinestyle{CStyle}{
    backgroundcolor=\color{cbackground},
    keywordstyle=\color{blue},
    stringstyle=\color{cstring},
    basicstyle=\ttfamily,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,              
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    language=C
}


\begin{document}
\title{Exercises 2.1}
\author{Learn C With Babbo}
\date{}
\maketitle
\begin{enumerate}
\item
In the line
\begin{lstlisting}[style=CStyle]
int my_var;
\end{lstlisting}
\verb|my_var| is being: \\
a) Declared, \\
b) Initialized, \\
c) Assigned, or \\
d) Pineapple?
\item
\verb|int| is called a(n): \\
a) Identifier \\
b) Variable \\
c) Data Type \\
d) 80s Sitcom
\item \verb|my_var| is a \rule{1cm}{0.15mm}, while its name is a(n) \rule{1cm}{0.15mm}: \\
a) Data Type, Literal \\
b) Literal, Identifier \\
c) Variable, Identifier \\
d) Variable, Literal
\item For each of the following, say whether \verb|my_var| is initialized. Then, if it was not, say whether it was 
declared, assigned, or both.
\begin{enumerate}
\item 
\begin{lstlisting}[style=CStyle]
int my_var;
\end{lstlisting}


\item 
\begin{lstlisting}[style=CStyle]
int my_var = 3;
\end{lstlisting}


\item
\begin{lstlisting}[style=CStyle]
int my_var;
my_var = 3;
\end{lstlisting}


\item 
\begin{lstlisting}[style=CStyle]
my_var = 3;
\end{lstlisting}

\end{enumerate}

\item What is the value of \verb|my_var| after the following line inside the \verb|main| function? 

\begin{lstlisting}[style=CStyle]
int my_var;
\end{lstlisting}

a) 0 \\
b) 1 \\
c) The code will not compile before \verb|my_var| is assigned. \\
d) The value of \verb|my_var| is unpredictable.

\item In the expression 

\begin{lstlisting}[style=CStyle]
int my_var = 3;
\end{lstlisting}

\verb|3| is called a(n): \\
a) \verb|int| variable \\
b) \verb|int| literal \\
c) \verb|int| datatype \\
d) \verb|int| elligent

\item After the execution of

\begin{lstlisting}[style=CStyle]
int my_var1 = 2;
int my_var2 = my_var1;
my_var1 = 4;
\end{lstlisting}
what is the value of \verb|my_var2|?

\item For each of the following, say whether it is a valid identifier or not. If it is not, give a reason why. \\
a) \verb|dataDyne| \\
b) \verb|iPhone| \\
c) \verb|2birds1stone| \\
d) \verb|two_birds_one_stone| \\
e) \verb|two_birds_1_stone| \\
f) \verb|Whoa!| \\
g) \verb|xwing@aliciousness| \\
h) \verb|_hi_|

\item Write a statement that prints the value of the \verb|int| variable \verb|my_var| followed by a new line.
\end{enumerate}

\end{document}